Perceptual symbol grounding in \\holographic memories

### 2016-11-07 papers/hrr-paper/paper.tex
Add a line break after every sentence for single-sentence changes in git
Added contrller text to .tex

	\subsection{Visual object classification}
	- SIFT + label
	\subsection{Localization and mapping}
	- SIFT + location
	\subsection{Holographic state machines (holographic controllers)}
	- sensory\_data + current\_state + next state
	\subsection{Reinforcement learning}
	- sensory\_data + action + reward
	\subsection{Language understanding}
	- TensorFlow (role) + word = question answering
	\subsection{Implicit inductive reasoning}

>>>>

	\subsection{Visual object classification}
	- SIFT + label
	\subsection{Localization and mapping}
	- SIFT + location
\subsection{Symbolic scripting (holographic controllers)}

We have used our system to demonstrate a mechanism for encoding neural programs and processes through series of associated action, perception and actuator symbols. We call this mechanism for defining controllers using holographic memories "symbolic scripting".

\begin{figure}[th!]
	\center
	\begin{subfigure}{1\columnwidth}
		\includegraphics[width=\columnwidth]{img/control_pipeline.png}
		\caption{Symbolic scripting pipeline}
		\label{fig:symbolic-scripting-a}
	\end{subfigure}

	\begin{subfigure}{0.7\columnwidth}
		\center
		\includegraphics[width=\columnwidth]{img/symbol_table.png}
		\caption{Symbol table}
		\label{fig:symbolic-scripting-b}
	\end{subfigure}
	\begin{subfigure}{1\columnwidth}
		\includegraphics[width=\columnwidth]{img/controller.png}
		\caption{Holographic program (script)}
		\label{fig:symbolic-scripting-c}
	\end{subfigure}
	\caption{Symbolic scripting example for light following behavior of a two-wheeled robot}
	\label{fig:symbolic-scripting}
\end{figure}

The basic idea is centered around symbolic representations of all three parts involved:
\begin{enumerate}
	\item \textbf{actions} are symbolic constants representing groups of control signals, such as "forward", "backward", "stop", "flex", etc.

	\item \textbf{actuators} are named controllable parts of the system on which actions can be performed on, such as "right\_wheel", "left\_wheel", etc.

	\item \textbf{senses} are preprocessed (classified) sensory stream labels, such as "bright", "dark", "touching", "falling\_down", "rolling", etc.
\end{enumerate}

An example of this kind of symbolic script is given on figure \ref{fig:symbolic-scripting}. Memory encodes light following behavior.

	\subsection{Reinforcement learning}
	- sensory\_data + action + reward
	\subsection{Language understanding}
	- TensorFlow (role) + word = question answering
	\subsection{Implicit inductive reasoning}
